Points Above Replacement

### 2022-04-26 Code/NBAPARCode.Rmd
Add files via upload

plot(league$VORP, scaledPAR, xlab = "VORP", ylab = "PAR", main = "Value Over Replacement Player vs. Points Above Replacement")
plot(league$WS, scaledPAR,  xlab = "WS", ylab = "PAR", main = "Win Shares vs. Points Above Replacement")
plot(league$BPM, scaledPAR, xlab = "BPM", ylab = "PAR", main = "Box Plus Minus vs. Points Above Replacement")
plot(league$PER, scaledPAR, xlab = "PER", ylab = "PAR", main = "Player Efficiency Rating vs. Points Above Replacement")
```

>>>>

pdf(file= "/Users/briankrikorian/Documents/GitHub/Spring2022Thesis/Manuscript/figs/VORPvsPAR.pdf", width = 6, height = 4)
plot(league$VORP, scaledPAR, xlab = "VORP", ylab = "PAR")
dev.off()

pdf(file= "/Users/briankrikorian/Documents/GitHub/Spring2022Thesis/Manuscript/figs/WSvsPAR.pdf", width = 6, height = 3.5)
plot(league$WS, scaledPAR,  xlab = "WS", ylab = "PAR")
dev.off()

pdf(file= "/Users/briankrikorian/Documents/GitHub/Spring2022Thesis/Manuscript/figs/BPMvsPAR.pdf", width = 6, height = 3.5)
plot(league$BPM, scaledPAR, xlab = "BPM", ylab = "PAR")
dev.off()

pdf(file= "/Users/briankrikorian/Documents/GitHub/Spring2022Thesis/Manuscript/figs/PERvsPAR.pdf", width = 6, height = 4)
plot(league$PER, scaledPAR, xlab = "PER", ylab = "PAR")
dev.off()
```
